\section{Experience}

\textbf{Raytheon \textbar\ Huntsville, AL} \\
{\small\textbf{FPGA Design Engineer II \textbar\ 05/2026 -- Present}} \\
{\small\textbf{FPGA Design Engineer I \textbar\ 07/2023 -- 01/2026}}

\begin{itemize}
  \item Implemented VHDL designs for image processing, RF communication and hardware test adapters targeting Xilinx 7000 series FPGAs, Ultrascale+ MPSoC and Versal devices.
  \item Designed bit-accurate simulation tests with Python/CoCoTB to verify DSP chains against reference models.
  \item Integrated firmware support for high-speed interfaces including PCIe and ethernet via bare-metal TCP/IP server.
  \item Wrote, debugged and emulated embedded diagnostic software applications in C/C++ with Vitis IDE and QEMU.
\end{itemize}

\textbf{Mercury Systems \textbar\ Huntsville, AL} \\
{\small\textbf{Firmware Engineer II \textbar\ 01/2026 -- 05/2026}}

\begin{itemize}
  \item Led firmware development supporting the Secure Processing Services team to deliver anti-tampering modules for server hardware.
  \item Architected a complete SoC build system to streamline integration of custom RTL designs and embedded software.
  \item Defined and adopted strict processes for version control, regression testing, and build deployment with CI/CD pipelines.
  \item Utilized Python, Git, CMake, Jenkins, and Artifactory to consolidate build configurations and guarantee reproducibility across a diverse team of engineers.
\end{itemize}

\textbf{Florida Polytechnic University \textbar\ Lakeland, FL} \\
{\small\textbf{Research Assistant \textbar\ 01/2023 -- 06/2023}}

\begin{itemize}
  \item Collaborated with researchers from Florida A\&M University to develop surgical robotics for bariatric endoscopy procedures.
  \item Studied realistic haptic feedback in control interfaces to maximize ease-of-use and patient safety funded by a multi-million dollar grant from the National Institutes of Health.
\end{itemize}
